---
title: "Introduction to U.S. Health Care"
linktitle: "M0: Getting started"
date: "2020-12-03"
start_date: "2021-01-26"
end_date: "2021-01-28"
menu:
  content:
    parent: Course Content
    weight: 1
type: docs
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

## Readings

- The [syllabus](/syllabus/), [content](/content/), and [assignments](/assignment/) pages for this class
- <i class="fas fa-book"></i> Read some book stuff
- <i class="fas fa-external-link-square-alt"></i> External links


## Slides {.tabset} 

The slides for this module are available online as HTML files. The goal of this module is to answer the key questions that anyone should want answered when they start to learn something new, "what, why, who, and how?". That is, "what are we learning and why?", "who is learning it?", and "how are we going to learn it?" 

The module is divided into subsections aligning with these core questions, each with its own set of slides. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

### 01: Why? 

Why are you taking this class? What's so interesting about health economics? Hopefully this part of our discussion convinces you how important and interesting health economics is. 

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/00-Introduction/00-intro1.html")
```

</center>

<p style="text-align:center;"><span class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/00-Introduction/00-intro1.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</span> <span class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/00-Introduction/00-intro1.pdf"><i class="far fa-file-pdf"></i> Download PDF of all slides</span></p>


### 02: What? 

Let's expand on the "why?" for a bit but also talk more specifically about the subjects we'll cover in this class. This section is the "what?".

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/00-Introduction/00-intro2.html")
```

<p style="text-align:center;"><span class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/00-Introduction/00-intro2.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</span> <span class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/00-Introduction/00-intro2.pdf"><i class="far fa-file-pdf"></i> Download PDF of all slides</span></p>


### 03: Who? 

Let's get to know each other a little!


### 04: How?

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/00-Introduction/00-intro4.html")
```

<p style="text-align:center;"><span class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/00-Introduction/00-intro4.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</span> <span class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/00-Introduction/00-intro4.pdf"><i class="far fa-file-pdf"></i> Download PDF of all slides</span></p>

