---
title: "Health Insurance"
linktitle: "M1: Health Insurance"
date: "2020-12-03"
start_date: "2021-01-26"
end_date: "2021-01-28"
menu:
  content:
    parent: Module Content
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

## Readings

- <i class="fas fa-book"></i> Sections 5.1-5.2 and 17.1 of [@pindyck2018], Chapter 4 of [@sloan2012], and [@einav2011]
- <i class="fas fa-external-link-square-alt"></i> CNN Business, February 2017, ["Humana pulls out of Obamacare for 2018"](https://money.cnn.com/2017/02/14/news/economy/humana-obamacare-insurer/)



## Slides

The goal of this module is to understand why people buy health insurance (or any insurance really) and how peoples' private information may influence health insurance prices (e.g., adverse selection). We'll finish the module with a discussion of current policy issues related to health insurance in the U.S.

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

### 01: Insurance and risk

How to we quantify risk and how does the presence of risk facilitate an insurance market?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/01-Insurance/01-insurance1.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance1.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance1.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>


### 02: Demand for health insurance

What underlying factors dictate our willingness to pay for health insurance?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/01-Insurance/01-insurance2.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance2.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance2.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>


### 03: Adverse selection 

What is adverse selection, and how does it affect health insurance markets?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/01-Insurance/01-insurance3.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance3.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance3.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>


### 04: Health insurance policy in the U.S.

The history of U.S. health insurance is pretty interesting, and it's important to know some of the history to understand how we got where we are today. For this final section, we'll talk about how health insurance started in the U.S. and where it is now.

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/01-Insurance/01-insurance4.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance4.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/01-Insurance/01-insurance4.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
