---
title: "Hospital Pricing and Competition"
linktitle: "M3: Competition"
date: "2020-12-03"
start_date: "2021-01-26"
end_date: "2021-01-28"
menu:
  content:
    parent: Module Content
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

## Readings

- <i class="fas fa-book"></i> Sections 5.4 of [@sloan2012], [@reinhardt2006], [@gaynor2015jel], and [@gaynor2017brookings]
- <i class="fas fa-external-link-square-alt"></i> 


## Slides

The goal of this module is to understand hospital pricing, how we measure competition (in general, but also some specific aspects of health care markets), and how competition affects hospital/insurer negotiations.

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

### 01: Pricing in a two-price market

Most of our intro economics models assume that firms set a single price. What happens if firms set prices in one market but are price-takers in an overlapping market?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/03-Pricing/03-comp1.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp1.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp1.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>


### 02: Prices and bargaining

In reality, hospitals bargain with insurers over their prices. How do we study pricing in this context?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/03-Pricing/03-comp2.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp2.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp2.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>


### 03: Hospital competition

What are the central issues when studying or measuring competition? What does the evidence say happens to hospital prices when competition changes?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/03-Pricing/03-comp3.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp3.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp3.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>


### 04: Mergers and prices

What's going on with hospital mergers? What's the difference between an "in-market" and "out-of-market" merger, and why does it matter?

<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ372-content/03-Pricing/03-comp4.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp4.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ372-content/03-Pricing/03-comp4.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
